---
title: "Getting Started" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>" 
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{Getting started} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=TRUE} 
library(echoannot)
```
 

# Import data  

To get the full dataset of all fine-mapped Parkinson's Disease loci, 
you can use the following function: 

```{r}
merged_DT <- echodata::get_Nalls2019_merged()
```

# Annotate 

Annotate SNP-wise fine-mapping results.

Here, we're only annotating a small number of SNPs high-confidence causal SNPs
for demo purposes.
The more SNPs you supply to `annotate_snps`, the longer it will take to 
query the selected databases for each SNP.

```{r}  
#### Only query high-confidence fine-mapping SNPs from one locus ####
dat <- merged_DT[Locus=="LRRK2" & Consensus_SNP==TRUE,]
#### Query annotations ####
dat_annot <- echoannot::annotate_snps(dat = dat,
                                      haploreg_annotation = TRUE, 
                                      regulomeDB_annotation = TRUE,
                                      biomart_annotation = TRUE) 
knitr::kable(dat_annot)
```


# Summary plots

## Credible Set bin plot

```{r} 
gg_cs_bin <- echoannot::CS_bin_plot(merged_DT = merged_DT,
                                    show_plot = FALSE)
```

## Credible Set counts plot

```{r}
gg_cs_counts <- echoannot::CS_counts_plot(merged_DT = merged_DT, 
                                          show_plot = FALSE)
```

## Epigenomic data

```{r}
gg_epi <- echoannot::peak_overlap_plot(
    merged_DT = merged_DT, 
    include.NOTT2019_enhancers_promoters = TRUE,
    include.NOTT2019_PLACseq = TRUE,
    #### Omit many annotations to save time ####
    include.NOTT2019_peaks = FALSE,
    include.CORCES2020_scATACpeaks = FALSE, 
    include.CORCES2020_Cicero_coaccess = FALSE, 
    include.CORCES2020_bulkATACpeaks = FALSE, 
    include.CORCES2020_HiChIP_FitHiChIP_coaccess = FALSE,
    include.CORCES2020_gene_annotations = FALSE)
```

## Super summary plot

Creates one big merged plot using the subfunctions above.

```{r, eval=FALSE} 
super_plot <- echoannot::super_summary_plot(merged_DT = merged_DT, 
                                            plot_missense = FALSE)

```

```{r Cleanup, include=FALSE}
remove(super_plot, gg_epi, gg_cs_counts, merged_DT) 
```


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

