---
title: "``r read.dcf('../DESCRIPTION', fields = 'Package')[1]``: Getting Started" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>" 
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{echoplot} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```

```R
library(`r pkg`)
```

# Merge and annotate 

## Import results 

Import pre-calculated fine-mapping results.

```{r}
dataset <- echodata::get_Nalls2019_loci(return_dir = TRUE)
```


Merge (and annotate) SNP-wise fine-mapping results.

```{r} 
merged_DT <- echoannot::merge_finemapping_results(dataset = dataset, 
                                                  minimum_support = 1,
                                                  haploreg_annotation = TRUE)
knitr::kable(head(merged_DT))
```

### Genome-wide example

To get the full dataset of al fine-mapped PD loci, you can use the following
function: 

```R
merged_DT <- echodata::get_Nalls2019_merged()

```

# Summary plots

## Credible Set bin plot

```{r} 
gg_cs_bin <- echoannot::CS_bin_plot(merged_DT = merged_DT)
```

## Credible Set counts plot

```{r}
gg_cs_counts <- echoannot::CS_counts_plot(merged_DT = merged_DT)
```

## Epigenomic data

```{r}
gg_epi <- echoannot::peak_overlap_plot(
    merged_DT = merged_DT, 
    include.NOTT2019_enhancers_promoters = TRUE,
    include.NOTT2019_PLACseq = TRUE,
    #### Omit many annotations to save time ####
    include.NOTT2019_peaks = FALSE,
    include.CORCES2020_scATACpeaks = FALSE, 
    include.CORCES2020_Cicero_coaccess = FALSE, 
    include.CORCES2020_bulkATACpeaks = FALSE, 
    include.CORCES2020_HiChIP_FitHiChIP_coaccess = FALSE,
    include.CORCES2020_gene_annotations = FALSE)
```

## Super summary plot

Creates one big merged plot using the subfunctions above.

```{r, eval=FALSE} 
super_plot <- echoannot::super_summary_plot(merged_DT = merged_DT, 
                                            plot_missense = FALSE)

```

```{r Cleanup, include=FALSE}
remove(super_plot, gg_epi, gg_cs_counts, merged_DT) 
```


# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

